Seminarium TI 3700\\ Data Analysis on Twitter(working title)

### 2014-03-19 authorinstr_2.tex
Intro Update

Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, where users can share short messages, called Tweets, with any other user. The limitation of 140 characters per Tweet forces users to compress all their information into a small message, making them extra interesting to analyze. These Tweets often contain information broadcasted by the user in the form of opinions, emotions, interests, etc. One of the biggest challenges is finding a way to extract the intended information from these Tweets. Once the information is extracted however, the possible applications are endless. This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. In the following section, Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, 
two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information. The first section will focus on single tweets, and the second section is focused on sets of multiple Tweets. Both of these sections will involve several usecases for certain techniques.

>>>>

Microblogging has grown out to become one of the most interesting forms of social media. Its most popular implementation has to be Twitter, 
where users can share short messages, called Tweets, with any other user. These short 140 character messages often contain valuable information about the user, their
interests, opinions, etc. This information can be very useful for a variety of applications, making social web data analytics an important field within
information technology. One of the biggest challenges is finding a way to extract the intended information from these Tweets. 
This paper is dedicated to giving an overview of successful techniques and useful applications of these social web data analytics. We will build up from
the basic techniques used by developers to collect tweets, to effective techniques that extract useful information from them. In the following section, 
Twitter's API gets introduced which will show that the platform already offers great tools and commands to retrieve specific datasets, or a completely random sample stream of Tweets. After that, 
two entire sections will be dedicated to all sorts of techniques that are being used to extract and analyze this information. The first section will focus on single tweets, and the second section is focused on sets of multiple Tweets. Both of these sections will involve several usecases for certain techniques.
